Untitled

### 2025-01-20 Scripts/Test_for_danielle.Rmd
tweakers

  for.tune.summary <- readRDS(paste0(loc,"/Results/forwards_fully_tuned_summary_no_age_correction_",what.2.tune,".Rds"))
  for.tune.all <- readRDS(paste0(loc,"/Results/forwards_fully_tuned_all_no_age_corection_res_",what.2.tune,".Rds"))

  load(file =  paste0(loc,"/Results/model_inputs_no_age_correction.Rdata"))
  # Get the stocks...
  Stocks <- names(for.tune.summary)
  n.stocks <- length(Stocks)

@@

  dub.time.summary <- data.frame(dub.time.summary)
  pop.dam <- data.frame(pop.dam)
  # saveRDS(pop.dam,paste0("D:/Github/ICM/Results/R0_and_gen_length_",what.2.tune,".Rds"))
  # saveRDS(dub.time.summary,paste0("D:/Github/ICM/Results/doubling_time_",what.2.tune,".Rds"))
  # saveRDS(for.tunes,paste0("D:/Github/ICM/Results/forward_tunes_for_figures_",what.2.tune,".Rds"))
  save(dub.time.summary,pop.dam,res.year.final,res.cohort.final,for.tunes,dub.time,for.tune.all,res.lambda.final,meta,meta.sub,
       file=paste0(loc,"/Results/all_cleaned_forward_tune_summaries_no_age_corection_",what.2.tune,".Rdata"))

  write.csv(meta.sub, paste0(loc,"/Data/metadata_no_age_corection.csv"))
} # end if load results
```

```{r clean-up-and-stats,include=F,echo=F,message=F,warning=F}
load(file=paste0(loc,"/Results/all_cleaned_forward_tune_summaries_no_age_corection_",what.2.tune,".Rdata"))
for.tune.summary <- readRDS(paste0(loc,"/Results/forwards_fully_tuned_summary_no_age_correction_",what.2.tune,".Rds"))

@@

save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Lambda_boxplot_6_species_",what.2.tune,".png"),new.lam.plt.6,base_width = 20,base_height = 10)

@@

save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Lambda_boxplot_other_species_",what.2.tune,".png"),new.lam.plt.others,base_width = 20,base_height = 10)

# # Standard deviation figure
# colrs.sd <- rep(c(rep('blue',4),rep('orange',4),rep('grey',4),rep('black',4)),20)
# pty.sd <- rep(rep(c(21,4,9,8),4),20)
# 
# lam.sd.plt <- ggplot(res.lambda.fin ) + 
#                                        geom_point(aes(y = lam.no.fish.sd,x=G.Species,group=Area.long,color=Area.long,shape = Area.long,fill=Area.long),size=3) +
#                                        scale_y_log10("Standard deviation (Lambda)",log_breaks(n=8)) +
#                                        scale_color_manual(values=colrs.sd) + scale_shape_manual(values = pty.sd) + scale_fill_manual(values=colrs.sd)+
#                                        theme(axis.text.x = element_text(angle =45,hjust=1),
#                                                  plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
# 
# save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Lambda_sd_",what.2.tune,".png"),lam.sd.plt,base_width = 10,base_height = 10)
#

@@

lam.sd.plt <- ggplot(res.chhp.summary,aes(y = avg.sd,x=locale,group=G.Species,color=G.Species)) + 
                                              geom_point(position=position_dodge(width=0.3),size=2) + 
                                              geom_line(position=position_dodge(width=0.3),size=1.25) +
                                              scale_color_manual(values=colrs.sd) + 
                                              geom_errorbar(aes(ymin=avg.sd - sd.of.sd, ymax=avg.sd+sd.of.sd,x=locale),width=0 ,position=position_dodge(width=0.3)) +
                                              xlab("") + ylab("Standard devation (Lambda)") + theme(legend.title = element_blank())
save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Lambda_sd_",what.2.tune,".png"),lam.sd.plt,base_width = 10,base_height = 6)

@@

save_plot(paste0(loc,"/Figures/tuned/No_age_correction/density_dependence_overall_",what.2.tune,".png"),dd.overall.combo,base_width = 10,base_height = 10)

@@

save_plot(paste0(loc,"/Figures/tuned/No_age_correction/density_dependence_nf_stocks_",what.2.tune,".png"),dd.stocks.nf.plt,base_width = 10,base_height = 10)

@@

save_plot(paste0(loc,"/Figures/tuned/No_age_correction/density_dependence_fish_stocks_",what.2.tune,".png"),dd.stocks.fish.plt,base_width = 10,base_height = 10)

@@

save_plot(paste0(loc,"/Figures/tuned/No_age_correction/R0_boxplot_6_species_",what.2.tune,".png"),r0.boxplt.6,base_width = 20,base_height = 10)

@@

save_plot(paste0(loc,"/Figures/tuned/No_age_correction/R0_boxplot_other_species_",what.2.tune,".png"),r0.boxplot.others,base_width = 20,base_height = 10)

@@

save_plot(paste0(loc,"/Figures/tuned/No_age_correction/r0_heatmap_nf_",what.2.tune,".png"),r0.heatmap,base_width = 20,base_height = 17)

@@

save_plot(paste0(loc,"/Figures/tuned/No_age_correction/r0_heatmap_fish_",what.2.tune,".png"),r0.heatmap.fish,base_width = 20,base_height = 17)

@@

save_plot(paste0(loc,"/Figures/tuned/No_age_correction/GL_boxplot_6_species_",what.2.tune,".png"),gen.boxplt.6,base_width = 20,base_height = 10)

@@

save_plot(paste0(loc,"/Figures/tuned/No_age_correction/GL_boxplot_other_species_",what.2.tune,".png"),gen.boxplt.others,base_width = 20,base_height = 10)

@@

save_plot(paste0(loc,"/Figures/tuned/No_age_correction/GL_heatmap_nf_",what.2.tune,".png"),gen.heatmap,base_width = 15,base_height = 10)

@@

save_plot(paste0(loc,"/Figures/tuned/No_age_correction/GL_heatmap_fish_",what.2.tune,".png"),gen.heatmap.fish,base_width = 15,base_height = 10)

@@

save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Doubling_time_heatmap_by_order_",what.2.tune,".png"),dub.heatmap,base_width = 20,base_height = 20)

@@

save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Doubling_time_time_series_",what.2.tune,".png"),dub.ts.plt,base_width = 10,base_height = 10)

@@

save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Doubling_time_sd_effects_",what.2.tune,".png"),p3,base_width = 11,base_height = 15)

@@

# save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Doubling_time_heatmap_by_sp6_",what.2.tune,".png"),dub.heatmap.sp6,base_width = 20,base_height = 17)

@@

# save_plot(paste0(loc,"/Figures/tuned/No_age_correction/lambda_timeseries_6_",what.2.tune,".png"),lambda.ts.plt,base_width = 12,base_height = 10)

@@

# save_plot(paste0(loc,"/Figures/tuned/No_age_correction/lambda_by_decade_6_",what.2.tune,".png"),lambda.dec.plt,base_width = 12,base_height = 12)

@@

# save_plot(paste0(loc,"/Figures/tuned/No_age_correction/lambda_no_fishing_6_",what.2.tune,".png"),lambda.plt,base_width = 12,base_height = 10)

@@

# save_plot(paste0(loc,"/Figures/tuned/No_age_correction/lambda_with_fishing_6_",what.2.tune,".png"),lambda.plt.fish,base_width = 12,base_height = 10)

@@

# 
# r0.ts.plt <- ggplot(pop.dam.6,aes(y=R0.opt,x=cohort,group=Stock.short,color=Stock.short,shape = Stock.short,fill = Stock.short)) + 
#                             geom_line(size=2)  + geom_point(size=4) +
#                             scale_y_log10(name = "Lifetime Reproductive Output") +
#                             facet_wrap(~G.Species) +
#                             scale_color_manual(name = "Stock",values = col.try) + scale_shape_manual(name = "Stock",values = pty) +
#                             scale_fill_manual(name = "Stock",values = col.try)+
#                             guides(colour = guide_legend(ncol = 1))+
#                             theme(axis.text.x = element_text(angle =45,hjust=1),legend.key.width = unit(5,'cm')) 
# r0.ts.plt
# 
# save_plot("D:/Github/ICM/Figures/tuned/R0_timeseries_6.png",r0.ts.plt,base_width = 30,base_height = 12)
# 
# r0.boxplt <- ggplot(pop.dam) + geom_boxplot(aes(y=R0.opt,x=Stock.no.species))  + 
#                             scale_y_log10(name = "Lifetime Reproductive Output")+#, breaks = c(0.001,0.01,0.1,1,5,10,50,100),minor_breaks = NULL) + 
#                             facet_wrap(~G.Species,scales = 'free')+
#                             theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none')
# r0.boxplt

# 
# windows(11,11)
# ggplot(pop.dam) + geom_boxplot(aes(y=gen.len.opt,x=Species)) + facet_wrap(~LME,scales='free_x') +
#                   ylab("Generation Length (years)") + theme(axis.text.x = element_text(angle =45,hjust=1))
# 
# windows(11,11)
# col.try <- rep(rep(c("black","blue","orange",'firebrick2','lightgreen'),3),20)
# lty <- rep(c(rep(1,5),rep(2,5),rep(4,5)),20)
# 
# gen.ts.plt <- ggplot(pop.dam.6,aes(y=gen.len.opt,x=cohort,group=Stock.short,color=Stock.short,linetype = Stock.short)) + 
#                             geom_line(size=2)  + 
#                             scale_y_log10(name = "Generation Length") +
#                             facet_wrap(~G.Species) +
#                             scale_color_manual(name = "Stock",values = col.try) + scale_linetype_manual(name = "Stock",values = lty) +
#                             guides(colour = guide_legend(ncol = 1))+
#                             theme(axis.text.x = element_text(angle =45,hjust=1),legend.key.width = unit(5,'cm')) 
# gen.ts.plt
# save_plot("D:/Github/ICM/Figures/tuned/Gen_time_series_6.png",gen.ts.plt,base_width = 20,base_height = 12)

@@

# save_plot("D:/Github/ICM/Figures/tuned/R0_ignoring_fishing.png",r0.plt,base_width = 8,base_height = 8)

@@

# #save_plot("D:/Github/ICM/Figures/tuned/R0_timeseries_ignoring_fishing.png",r0.plt,base_width = 8,base_height = 8)

@@

# save_plot("D:/Github/ICM/Figures/tuned/Percentage_change_to_bycatch_by_species.png",bycatch.plt,base_width = 8,base_height = 8)

@@

# save_plot("D:/Github/ICM/Figures/tuned/Percentage_change_to_bycatch_by_cod_stock.png",bycatch.plt.cod,base_width = 8,base_height = 8)

>>>>

  #for.tune.summary <- readRDS(paste0(loc,"/Results/forwards_fully_tuned_summary_no_age_correction_",what.2.tune,".Rds"))
  #for.tune.all <- readRDS(paste0(loc,"/Results/forwards_fully_tuned_all_no_age_corection_res_",what.2.tune,".Rds"))

  #load(file =  paste0(loc,"/Results/model_inputs_no_age_correction.Rdata"))
  # Get the stocks...
  Stocks <- names(for.tune.summary)
  n.stocks <- length(Stocks)

@@

  dub.time.summary <- data.frame(dub.time.summary)
  pop.dam <- data.frame(pop.dam)
  # saveRDS(pop.dam,paste0("D:/Github/ICM/Results/R0_and_gen_length_",what.2.tune,".Rds"))
  # saveRDS(dub.time.summary,paste0("D:/Github/ICM/Results/doubling_time_",what.2.tune,".Rds"))
  # saveRDS(for.tunes,paste0("D:/Github/ICM/Results/forward_tunes_for_figures_",what.2.tune,".Rds"))
  #save(dub.time.summary,pop.dam,res.year.final,res.cohort.final,for.tunes,dub.time,for.tune.all,res.lambda.final,meta,meta.sub,
  #     file=paste0(loc,"/Results/all_cleaned_forward_tune_summaries_no_age_corection_",what.2.tune,".Rdata"))

  #write.csv(meta.sub, paste0(loc,"/Data/metadata_no_age_corection.csv"))
} # end if load results
```

```{r clean-up-and-stats,include=F,echo=F,message=F,warning=F}
#load(file=paste0(loc,"/Results/all_cleaned_forward_tune_summaries_no_age_corection_",what.2.tune,".Rdata"))
#for.tune.summary <- readRDS(paste0(loc,"/Results/forwards_fully_tuned_summary_no_age_correction_",what.2.tune,".Rds"))

@@

##save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Lambda_boxplot_6_species_",what.2.tune,".png"),new.lam.plt.6,base_width = 20,base_height = 10)

@@

##save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Lambda_boxplot_other_species_",what.2.tune,".png"),new.lam.plt.others,base_width = 20,base_height = 10)

# # Standard deviation figure
# colrs.sd <- rep(c(rep('blue',4),rep('orange',4),rep('grey',4),rep('black',4)),20)
# pty.sd <- rep(rep(c(21,4,9,8),4),20)
# 
# lam.sd.plt <- ggplot(res.lambda.fin ) + 
#                                        geom_point(aes(y = lam.no.fish.sd,x=G.Species,group=Area.long,color=Area.long,shape = Area.long,fill=Area.long),size=3) +
#                                        scale_y_log10("Standard deviation (Lambda)",log_breaks(n=8)) +
#                                        scale_color_manual(values=colrs.sd) + scale_shape_manual(values = pty.sd) + scale_fill_manual(values=colrs.sd)+
#                                        theme(axis.text.x = element_text(angle =45,hjust=1),
#                                                  plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))
# 
# #save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Lambda_sd_",what.2.tune,".png"),lam.sd.plt,base_width = 10,base_height = 10)
#

@@

lam.sd.plt <- ggplot(res.chhp.summary,aes(y = avg.sd,x=locale,group=G.Species,color=G.Species)) + 
                                              geom_point(position=position_dodge(width=0.3),size=2) + 
                                              geom_line(position=position_dodge(width=0.3),size=1.25) +
                                              scale_color_manual(values=colrs.sd) + 
                                              geom_errorbar(aes(ymin=avg.sd - sd.of.sd, ymax=avg.sd+sd.of.sd,x=locale),width=0 ,position=position_dodge(width=0.3)) +
                                              xlab("") + ylab("Standard devation (Lambda)") + theme(legend.title = element_blank())
##save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Lambda_sd_",what.2.tune,".png"),lam.sd.plt,base_width = 10,base_height = 6)

@@

##save_plot(paste0(loc,"/Figures/tuned/No_age_correction/density_dependence_overall_",what.2.tune,".png"),dd.overall.combo,base_width = 10,base_height = 10)

@@

##save_plot(paste0(loc,"/Figures/tuned/No_age_correction/density_dependence_nf_stocks_",what.2.tune,".png"),dd.stocks.nf.plt,base_width = 10,base_height = 10)

@@

#save_plot(paste0(loc,"/Figures/tuned/No_age_correction/density_dependence_fish_stocks_",what.2.tune,".png"),dd.stocks.fish.plt,base_width = 10,base_height = 10)

@@

#save_plot(paste0(loc,"/Figures/tuned/No_age_correction/R0_boxplot_6_species_",what.2.tune,".png"),r0.boxplt.6,base_width = 20,base_height = 10)

@@

#save_plot(paste0(loc,"/Figures/tuned/No_age_correction/R0_boxplot_other_species_",what.2.tune,".png"),r0.boxplot.others,base_width = 20,base_height = 10)

@@

#save_plot(paste0(loc,"/Figures/tuned/No_age_correction/r0_heatmap_nf_",what.2.tune,".png"),r0.heatmap,base_width = 20,base_height = 17)

@@

#save_plot(paste0(loc,"/Figures/tuned/No_age_correction/r0_heatmap_fish_",what.2.tune,".png"),r0.heatmap.fish,base_width = 20,base_height = 17)

@@

#save_plot(paste0(loc,"/Figures/tuned/No_age_correction/GL_boxplot_6_species_",what.2.tune,".png"),gen.boxplt.6,base_width = 20,base_height = 10)

@@

#save_plot(paste0(loc,"/Figures/tuned/No_age_correction/GL_boxplot_other_species_",what.2.tune,".png"),gen.boxplt.others,base_width = 20,base_height = 10)

@@

#save_plot(paste0(loc,"/Figures/tuned/No_age_correction/GL_heatmap_nf_",what.2.tune,".png"),gen.heatmap,base_width = 15,base_height = 10)

@@

#save_plot(paste0(loc,"/Figures/tuned/No_age_correction/GL_heatmap_fish_",what.2.tune,".png"),gen.heatmap.fish,base_width = 15,base_height = 10)

@@

#save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Doubling_time_heatmap_by_order_",what.2.tune,".png"),dub.heatmap,base_width = 20,base_height = 20)

@@

#save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Doubling_time_time_series_",what.2.tune,".png"),dub.ts.plt,base_width = 10,base_height = 10)

@@

#save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Doubling_time_sd_effects_",what.2.tune,".png"),p3,base_width = 11,base_height = 15)

@@

# #save_plot(paste0(loc,"/Figures/tuned/No_age_correction/Doubling_time_heatmap_by_sp6_",what.2.tune,".png"),dub.heatmap.sp6,base_width = 20,base_height = 17)

@@

# #save_plot(paste0(loc,"/Figures/tuned/No_age_correction/lambda_timeseries_6_",what.2.tune,".png"),lambda.ts.plt,base_width = 12,base_height = 10)

@@

# #save_plot(paste0(loc,"/Figures/tuned/No_age_correction/lambda_by_decade_6_",what.2.tune,".png"),lambda.dec.plt,base_width = 12,base_height = 12)

@@

# #save_plot(paste0(loc,"/Figures/tuned/No_age_correction/lambda_no_fishing_6_",what.2.tune,".png"),lambda.plt,base_width = 12,base_height = 10)

@@

# #save_plot(paste0(loc,"/Figures/tuned/No_age_correction/lambda_with_fishing_6_",what.2.tune,".png"),lambda.plt.fish,base_width = 12,base_height = 10)

@@

# 
# r0.ts.plt <- ggplot(pop.dam.6,aes(y=R0.opt,x=cohort,group=Stock.short,color=Stock.short,shape = Stock.short,fill = Stock.short)) + 
#                             geom_line(size=2)  + geom_point(size=4) +
#                             scale_y_log10(name = "Lifetime Reproductive Output") +
#                             facet_wrap(~G.Species) +
#                             scale_color_manual(name = "Stock",values = col.try) + scale_shape_manual(name = "Stock",values = pty) +
#                             scale_fill_manual(name = "Stock",values = col.try)+
#                             guides(colour = guide_legend(ncol = 1))+
#                             theme(axis.text.x = element_text(angle =45,hjust=1),legend.key.width = unit(5,'cm')) 
# r0.ts.plt
# 
# #save_plot("D:/Github/ICM/Figures/tuned/R0_timeseries_6.png",r0.ts.plt,base_width = 30,base_height = 12)
# 
# r0.boxplt <- ggplot(pop.dam) + geom_boxplot(aes(y=R0.opt,x=Stock.no.species))  + 
#                             scale_y_log10(name = "Lifetime Reproductive Output")+#, breaks = c(0.001,0.01,0.1,1,5,10,50,100),minor_breaks = NULL) + 
#                             facet_wrap(~G.Species,scales = 'free')+
#                             theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none')
# r0.boxplt

# 
# windows(11,11)
# ggplot(pop.dam) + geom_boxplot(aes(y=gen.len.opt,x=Species)) + facet_wrap(~LME,scales='free_x') +
#                   ylab("Generation Length (years)") + theme(axis.text.x = element_text(angle =45,hjust=1))
# 
# windows(11,11)
# col.try <- rep(rep(c("black","blue","orange",'firebrick2','lightgreen'),3),20)
# lty <- rep(c(rep(1,5),rep(2,5),rep(4,5)),20)
# 
# gen.ts.plt <- ggplot(pop.dam.6,aes(y=gen.len.opt,x=cohort,group=Stock.short,color=Stock.short,linetype = Stock.short)) + 
#                             geom_line(size=2)  + 
#                             scale_y_log10(name = "Generation Length") +
#                             facet_wrap(~G.Species) +
#                             scale_color_manual(name = "Stock",values = col.try) + scale_linetype_manual(name = "Stock",values = lty) +
#                             guides(colour = guide_legend(ncol = 1))+
#                             theme(axis.text.x = element_text(angle =45,hjust=1),legend.key.width = unit(5,'cm')) 
# gen.ts.plt
# #save_plot("D:/Github/ICM/Figures/tuned/Gen_time_series_6.png",gen.ts.plt,base_width = 20,base_height = 12)

@@

# #save_plot("D:/Github/ICM/Figures/tuned/R0_ignoring_fishing.png",r0.plt,base_width = 8,base_height = 8)

@@

# ##save_plot("D:/Github/ICM/Figures/tuned/R0_timeseries_ignoring_fishing.png",r0.plt,base_width = 8,base_height = 8)

@@

# #save_plot("D:/Github/ICM/Figures/tuned/Percentage_change_to_bycatch_by_species.png",bycatch.plt,base_width = 8,base_height = 8)

@@

# #save_plot("D:/Github/ICM/Figures/tuned/Percentage_change_to_bycatch_by_cod_stock.png",bycatch.plt.cod,base_width = 8,base_height = 8)
